---
title: "renv"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{renv}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(riskassessment)
```

# Overview

The `renv` package provides project-local R dependency management to your projects.  
It helps manage library paths (and other project-specific state) to help isolate your project’s R dependencies.  
The `renv` package helps you create **r**eproducible **env**ironments for your R projects.  
It will make your R packages more **isolated**, **portable** and **reproducable**.

## How to use it

First one has to initialize a new project-local environment with a private R library - which can be done via `renv::init()`.
Afterwards, work in the project as usual and save the current state of the project library with `renv::snapshot()`.
This result will be saved into a lockfile - named `renv.lock`.
Now, continue working on your project and call `renv::snapshot()` again, in order to update the project state - or with `renv::restore()`, revert the previous state if you have encountered problems while developing.

## How to ignore files in the lock file

By default `renv` ignores all files stated in the `.gitignore` file. If you want to extend that further, you can use a `.renvignore` file - which is specified similar to the `.gitignore` file.
The `lockfile` will only be upgraded in case of need for very important features as the development team wants to keep a stable version at any given time.

## Cache Location on different Operating Systems

*Linux	`~/.local/share/renv`
*macOS	`~/Library/Application Support/renv`
*Windows	`%LOCALAPPDATA%/renv`

## References
* [github.io/renv/](https://rstudio.github.io/renv/)
* [Introduction to renv](https://rstudio.github.io/renv/articles/renv.html)