---
title: '<span style=''color: steelblue;''>R Packages Risk Assessment </span>'
author: '**Author (Role): `r params$username` (`r params$user_role `)**'
date: "**Report Date: `r format(Sys.time(), '%B %d, %Y')`**"
output:
  word_document
params:
  package: NA
  riskmetric_version: NA
  cwd: NA
  username: NA
  user_role: NA
always_allow_html: yes
---


```{r echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

setwd(params$cwd)

pkg_GenInfo = dbSelect(glue("SELECT * FROM package WHERE name ='{params$package}'"))

package_id <- dbSelect(glue(
  "SELECT id
FROM package
WHERE name = '{params$package}';"))

if(nrow(package_id) == 0)
  loggit("ERROR", paste0("Package with id ", package_id, "was not found while
                         generating a docx report."))

# Collect all the metric names and values associated to package_id.
values$riskmetrics_mm <- dbSelect(glue(
  "SELECT metric.name, package_metrics.value
FROM metric
INNER JOIN package_metrics ON metric.id = package_metrics.metric_id
WHERE package_metrics.package_id = '{package_id}' AND metric.class = 'maintenance' ;"))

for(i in 1:nrow(values$riskmetrics_mm))
  values[[values$riskmetrics_mm$name[i]]] <- values$riskmetrics_mm$value[i]

riskmetrics_cum <- dbSelect(glue(
  "SELECT *
FROM community_usage_metrics
WHERE id = '{params$package}'"))

pkgs_in_db <- dbSelect(glue("SELECT id FROM community_usage_metrics"))

riskmetrics_cum <- dbSelect(glue(
  "SELECT *
FROM community_usage_metrics
WHERE id ='{params$package}'"))

time_since_first_release_info <- riskmetrics_cum$time_since_first_release[1] 
time_since_version_release_info <-riskmetrics_cum$time_since_version_release[1]
no_of_downloads_last_year_info <- riskmetrics_cum$no_of_downloads_last_year[1]

metric_id <- dbSelect(glue("SELECT id FROM metric WHERE name = 'covr_coverage';"))

# covr_coverage <- dbSelect(glue(
# "SELECT value
# FROM package_metrics
# WHERE package_id = '{package_id}'
# AND metric_id = '{metric_id}'"))
# 
# covr_coverage <- covr_coverage$value

# Gather overall comments.
comment_o <- dbSelect(glue(
  "SELECT *
FROM comments
WHERE id = '{params$package}' AND comment_type = 'o'"))

# Gather maintenance metrics comments.
comment_mm <- dbSelect(glue(
  "SELECT user_name, user_role, comment, added_on
FROM comments WHERE id = '{params$package}'
AND comment_type = 'mm'"))

# Gather community usage metrics comments.
comment_cum <- dbSelect(glue(
  "SELECT user_name, user_role, comment, added_on
FROM comments WHERE id = '{params$package}' AND comment_type = 'cum'"))

# Gather test metric comments.
comment_tm <- dbSelect(glue(
  "SELECT user_name, user_role, comment, added_on
FROM comments WHERE id = '{params$package}' AND comment_type = 'tm'"))

```

## Report for "`r pkg_GenInfo$name`" package

This report was generated using riskmetric version **`r params$riskmetric_version`**. Metrics were reviewed via the R Packages Risk Assessment Application.</div>

```{r setup, include=FALSE}
library(knitr)
library(shiny)

knitr::opts_chunk$set(echo = F, fig.width = 5.5, fig.height = 3.4)
```

<hr style="
height: 2px;
border: none;
color: #3c8dbc;
background-color: #3c8dbc">

**Summary**

Score: `r pkg_GenInfo$score`
```{r echo=FALSE}
if (!identical(pkg_GenInfo$decision, character(0)) && pkg_GenInfo$decision != "") {
  HTML(glue("<br><h5>Overall risk: <b>{pkg_GenInfo$decision}</b></h5>"))
} else{
  HTML(glue("<br><h5><b>Overall risk: Pending</b></h5>"))
}
```


**Overall Comments(`r nrow(comment_o)`):**

```{r echo=FALSE}
comment_o <- data.frame(comment_o %>% map(rev))
table_o <- data.frame(
  "User ID"  = comment_o$user_name,
  "Role"     = comment_o$user_role,
  "Time"     = comment_o$added_on,
  "Comments" =comment_o$comment)

knitr::kable(table_o, format = 'pandoc')
```
\newpage

## General Info

**Package:** `r pkg_GenInfo$name`

**Version:** `r pkg_GenInfo$version`

**Title:** `r pkg_GenInfo$title`

**Description:** `r pkg_GenInfo$description`

**Author:** `r pkg_GenInfo$author`

**Maintainer:** `r pkg_GenInfo$maintainer`

**License:** `r pkg_GenInfo$license`

**Published:** `r pkg_GenInfo$published`

\newpage

## Maintenance Metrics

```{r echo=FALSE}

Metric <- c("Presence of vignettes?",
            "Associated website URL?",
            "NEWS?",
            "News is current?",
            "Bugs publicly documented?",
            "Bug closure",
            "Documentation",
            "Source code public?",
            "Has a maintainer?")

Result <- c(
  if(values$has_vignettes %in% c("NA", "pkg_metric_error")){"NA"}
  else{ifelse(values$has_vignettes != "0", "YES", "NO")},
  
  if(values$has_website == "pkg_metric_error"){"NA"}
  else{ifelse(values$has_website != "NA", "YES", "NO")},
  
  if(values$has_news %in% c("NA", "pkg_metric_error")){"NA"}
  else{ ifelse(values$has_news == "1", "YES", "NO")},
  
  if(values$news_current %in% c("NA", "pkg_metric_error")){"NA"}
  else{ifelse(values$news_current == "TRUE", "YES", "NO")},
  
  if(values$has_bug_reports_url == "pkg_metric_error"){"NA"}
  else{ifelse(values$has_bug_reports_url == "NA", "NO", "YES")},
  
  if(values$bugs_status %in% c("NA", "pkg_metric_error")){"NA"}
  else{paste0(values$bugs_status, "%")},
  
  if(values$export_help %in% c("NA", "pkg_metric_error")){"NA"}
  else{paste0(values$export_help, "%")},
  
  if(values$has_source_control == "pkg_metric_error"){"NA"}
  else{ ifelse(values$has_source_control == "NA", "NO", "YES")},
  
  if(values$has_maintainer %in% c("NA", "pkg_metric_error")){"NA"}
  else{ ifelse(values$has_maintainer != "", "YES", "NO")}
)

Detail <- c(
  if(values$has_vignettes %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    paste("The package has", values$has_vignettes,
          if(values$has_vignettes == "1") "vignette" else "vignettes"),
  
  if(values$has_website %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    ifelse(values$has_website != "NA", paste("Website:", values$has_website),
           "The package does not have an associated website URL"),
  
  if(values$has_news %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    paste("The package",
          ifelse(values$has_news == "1", "has", "does not have"),
          "a NEWS file"),
  
  if(values$news_current %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    paste("NEWS file",
          ifelse(values$news_current == "TRUE", "contains", "does not contain"),
          "an entry for the current version number"),
  
  if(values$has_bug_reports_url == "pkg_metric_error")
    "Metric is not applicable for this source of package"
  else
    ifelse(values$has_bug_reports_url != "NA",
           paste("Bug reports URL:", values$has_bug_reports_url),
           "The bugs are not publicly documented"),
  
  if(values$bugs_status %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    "Percentage of last 30 bugs closed",
  
  if(values$export_help %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else{"Percentage of exported objects documented"},
  
  if(values$has_source_control == "pkg_metric_error")
    "Metric is not applicable for this soucre of package"
  else
    ifelse(values$has_source_control != "NA",
           paste("Source code URL:", values$has_source_control ),
           "Package does not have a source code URL"),
  
  if(values$has_maintainer %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this soucre of package"
  else
    ifelse(values$has_maintainer != "",
           values$has_maintainer,
           "Package does not have a maintainer")
)

table_infobox <- data.frame(Metric, Result, Detail)
knitr::kable(table_infobox, format = 'pandoc')
```

### Comments for Maintenance Metrics(`r nrow(comment_mm)`):

```{r echo=FALSE}
comment_mm <- data.frame(comment_mm %>% map(rev))

table_mm <- data.frame(
  "User ID" = comment_mm$user_name,
  "Role" = comment_mm$user_role,
  "Time" = comment_mm$added_on,
  "Comments" = comment_mm$comment)

knitr::kable(table_mm, format='pandoc')
```

\newpage

## Community Usage Metrics

```{r echo=FALSE}

Metric <- c("Package Maturity", "Version Maturity", "Download Count")

Result <- c(
  if(time_since_first_release_info == -1){"NA"}
  else{time_since_first_release_info},
  if(time_since_version_release_info == -1){"NA"}
  else{time_since_version_release_info},
  if(no_of_downloads_last_year_info == -1){"NA"}
  else{formatC(no_of_downloads_last_year_info, format="f", big.mark=",", digits=0)}
)

Detail <- c(
  if(time_since_first_release_info == -1){"Metric is not applicable for this source of package"}
  else{"Months since first release."},
  if(time_since_version_release_info == -1){"Metric is not applicable for this source of package"}
  else{"Months since version release."},
  if(no_of_downloads_last_year_info == -1){"Metric is not applicable for this source of package"}
  else{"Downloads in Last Year."}
)

table_infobox_cum<-data.frame(Metric, Result, Detail)

knitr::kable(table_infobox_cum, format='pandoc')

num_dwnlds_plot(
  data = riskmetrics_cum,
  input_select_pack = params$package)
```

### Comments for Community Usage Metrics(`r nrow(comment_cum)`):

```{r echo=FALSE}
comment_cum <- data.frame(comment_cum %>% map(rev))

table_cum <- data.frame(
  "User ID" = comment_cum$user_name,
  "Role" = comment_cum$user_role,
  "Time" = comment_cum$added_on,
  "Comments" = comment_cum$comment)

knitr::kable(table_cum, format ='pandoc')
```
<!--

\newpage
## Testing Metrics


# ```{r echo=FALSE}
#   bands = data.frame(
#     start = c(0, 40, 80),
#     end = c(40, 80, 100),
#     color = ifelse(covr_coverage != "pkg_metric_error",
#                    c("#ea3838", "#ffac29", "#00CC00"),
#                    c("#808080", "#808080", "#808080")),
#     stringsAsFactors = FALSE
#   )
#   bands2 = data.frame(
#     start = c(0, 40, 80),
#     end = c(40, 80, 100),
#     color = ifelse(covr_coverage != "pkg_metric_error",
#                    c("#ea3838", "#ffac29", "#00CC00"),
#                    c("#808080", "#808080", "#808080")),
#     stringsAsFactors = FALSE
#   )
#   amAngularGauge(
#     x = as.numeric(ifelse(covr_coverage == "NA", 0, covr_coverage)),
#     start = 0,
#     end = 100,
#     bands = bands,
#     secondAxe = TRUE,
#     start2 = 0,
#     end2 = 100,
#     bands2 = bands2
#   )
# ```
-->

<!-- ### Comments for Testing Metrics(`r nrow(comment_tm)`):  -->

<!-- ```{r echo=FALSE} -->
<!-- comment_tm <- data.frame(comment_tm %>% map(rev)) -->
<!-- table_tm<-data.frame("User ID"=comment_tm$user_name,"Role"= comment_tm$user_role, "Time"= comment_tm$added_on,"Comments"=comment_tm$comment) -->
<!--  knitr::kable(table_tm, format='pandoc') -->
<!-- ``` -->
