---
title: '<span style=''color: steelblue;''>R Package Risk Assessment </span>'
author: '**Author (Role): `r input$name` (`r input$role `)**'
date: "**Report Date: `r format(Sys.time(), '%B %d, %Y')`**"
output:
  word_document
params:
  cwd: NA
  package: NA
subtitle: R Validation Hub
always_allow_html: yes
---


```{r  echo=FALSE,warning=FALSE }

setwd(params$cwd)

res4 = db_fun(paste0(
  "SELECT * FROM Packageinfo WHERE package ='",
  params$package,
  "'"
))

comment_o <-
  db_fun(
    paste0(
      "SELECT * FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'o'"
    )
  )

  values$riskmetrics_tm <-
    db_fun(
      paste0(
        "SELECT * FROM TestMetrics WHERE TestMetrics.tm_id ='",
        input$select_pack,
        "'"
      )
    )
  values$riskmetrics_tm <- c(strsplit(values$riskmetrics_tm$test_coverage,",")[[1]][1], strsplit(values$riskmetrics_tm$test_coverage,",")[[1]][2])
 riskmetrics_cum <-
    db_fun(
      paste0(
        "SELECT * FROM CommunityUsageMetrics WHERE cum_id ='",
        params$package,
        "'"
      )
    )
 
   pkgs_in_db <- db_fun(paste0("SELECT cum_id FROM CommunityUsageMetrics"))
  
  if (!(params$package %in% pkgs_in_db$cum_id)) {
    metric_cum_Info_upload_to_DB(params$package)
    riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
  } else{
    riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
  }
   
  # Load the data table column into a reactive variable for time since first release.
  values$time_since_first_release_info <- riskmetrics_cum$time_since_first_release[1] 
  values$time_since_version_release_info <-riskmetrics_cum$time_since_version_release[1]
  values$riskmetrics_mm <-
    db_fun(
      paste(
        "SELECT * FROM MaintenanceMetrics WHERE MaintenanceMetrics.mm_id ='",
        params$package,
        "'",
        sep = ""
      )
    )
   
  values$package_has_vignettes <- c(strsplit(values$riskmetrics_mm$package_has_vignettes,",")[[1]][1], strsplit(values$riskmetrics_mm$package_has_vignettes,",")[[1]][2])
  values$package_has_website <- c(strsplit(values$riskmetrics_mm$package_has_website,",")[[1]][1], strsplit(values$riskmetrics_mm$package_has_website,",")[[1]][2])
  values$package_has_news <- c(strsplit(values$riskmetrics_mm$package_has_news,",")[[1]][1], strsplit(values$riskmetrics_mm$package_has_news,",")[[1]][2])
  values$news_is_current <- c(strsplit(values$riskmetrics_mm$news_is_current,",")[[1]][1], strsplit(values$riskmetrics_mm$news_is_current,",")[[1]][2])
  values$has_bug_reports <- c(strsplit(values$riskmetrics_mm$has_bug_reports,",")[[1]][1], strsplit(values$riskmetrics_mm$has_bug_reports,",")[[1]][2])
  values$status_of_last_30_reported_bugs <- c(strsplit(values$riskmetrics_mm$status_of_last_30_reported_bugs,",")[[1]][1], strsplit(values$riskmetrics_mm$status_of_last_30_reported_bugs,",")[[1]][2])
  values$exported_objects_with_documentation <- c(strsplit(values$riskmetrics_mm$exported_objects_with_documentation,",")[[1]][1], strsplit(values$riskmetrics_mm$exported_objects_with_documentation,",")[[1]][2])
  values$source_code_is_public <- c(strsplit(values$riskmetrics_mm$source_code_is_public,",")[[1]][1], strsplit(values$riskmetrics_mm$source_code_is_public,",")[[1]][2])
  values$has_a_package_maintainer <- c(strsplit(values$riskmetrics_mm$has_a_package_maintainer,",")[[1]][1], strsplit(values$riskmetrics_mm$has_a_package_maintainer,",")[[1]][2])
  
  
 comment_mm2 <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'mm'"
        )
      )  

    comment_tm2 <-
      db_fun(
        paste(
          "SELECT user_name, user_role, comment, added_on FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'tm'",
          sep = ""
        )
      )

    comment_mm2 <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'mm'"
        )
      )

    comment_cum2 <-
      db_fun(
        paste(
          "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'cum'",
          sep = ""
        )
      )

```

## Report of the " `r res4$package` " Package: 

This **`r res4$package`** package report was generated using  **`r input$select_ver`** riskmetric version .  Metrics were reviewed via the R Package Risk Assessment Application.</div>



```{r setup, include=FALSE}
library(knitr)
library(shiny)

knitr::opts_chunk$set(echo = F,fig.width=5.5, fig.height=3.4)

#Plot parameters
#define base_size of text
bsize_text <- 11

#define background color of plots
p_color <- 'white'

```


<hr style="
  height: 2px;
  border: none;
  color: #3c8dbc;
  background-color: #3c8dbc">



**Summary**

Score: `r values$selected_pkg$score`
```{r echo=FALSE}
 if (!identical(values$selected_pkg$decision, character(0)) && values$selected_pkg$decision != "") {
       if(values$selected_pkg$decision == "Accept"){
      HTML(paste("<br>", "<h3>Decision: ", "<b>Accepted</b></h3>"))
    }else{
      HTML(paste("<br>", "<h3>Decision: ", "<b>Rejected</b></h3>"))
    }
  } else{
    HTML(paste("<br>", "<h5><b>Decision: Pending</b></h5>"))
  }
```


**Overall Comments(`r nrow(comment_o)`):**

```{r echo=FALSE}
  comment_o <- data.frame(comment_o %>% map(rev))
table_o<-data.frame("User ID"=comment_o$user_name,"Role"= comment_o$user_role, "Time"= comment_o$added_on,"Comments"=comment_o$comment)
  
knitr::kable(table_o, format='pandoc')
  
```

## General Info

**Package:** `r res4$package`

**Version:** `r res4$version`

**Title:** `r res4$title`

**Description:** `r res4$description`

**Author:** `r res4$author`

**Maintainer:** `r res4$maintainer`

**License:** `r res4$license`

**Published:** `r res4$published`


## Maintenance Metrics

```{r echo=FALSE}

Metric<-c("Presence of vignettes?","Associated website URL?","NEWS?","News is current?","Bugs publicly documented?","Bug closure","Documentation","Source code public?","Has a maintainer?")

Result<-c(
    if(values$package_has_vignettes[2] == -1){"NA"}
      else{ ifelse(values$package_has_vignettes[1] == 1, "YES", "NO")},
     if(values$package_has_website[2] == -1){"NA"}
      else{ ifelse(values$package_has_website[1] == 1, "YES", "NO")},
     if(values$package_has_news[2] == -1){"NA"}
      else{ ifelse(values$package_has_news[1] == 1, "YES", "NO")},
      if(values$news_is_current[2] == -1){"NA"}
      else{ ifelse(values$news_is_current[1] == 1, "YES", "NO")},
     if(values$has_bug_reports[2] == -1){"NA"}
      else{ ifelse(values$has_bug_reports[1] == 1, "YES", "NO")},
     if(values$status_of_last_30_reported_bugs[2] == -1){"NA"}
      else{paste0(values$status_of_last_30_reported_bugs[1],"%")},
     if(values$exported_objects_with_documentation[2] == -1){"NA"}
      else{paste0(values$exported_objects_with_documentation[1],"%")},
     if(values$source_code_is_public[2] == -1){"NA"}
      else{ ifelse(values$source_code_is_public[1] == 1, "YES", "NO")},
     if(values$has_a_package_maintainer[2] == -1){"NA"}
      else{ ifelse(values$has_a_package_maintainer[1] == 1, "YES", "NO")}
    )

Detail<-c(
          if(values$package_has_vignettes[2] == -1){"Metric is not applicable for this source of package"}
            else{paste("The package has", values$package_has_vignettes[2], "Vignettes")},
          if(values$package_has_website[2] == -1){"Metric is not applicable for this source of package"}
            else{ ifelse(values$package_has_website[1] == 1, paste("Website:",values$package_has_website[2]), "The package does not have an associated website URL")},
          if(values$package_has_news[2] == -1){"Metric is not applicable for this source of package"}
            else{ ifelse(values$package_has_news[1] == 1, "The package has a NEWS file.", "The package does not have a NEWS file")},
          if(values$news_is_current[2] == -1){"Metric is not applicable for this source of package"}
            else{ ifelse(values$news_is_current[1] == 1, "NEWS file contains entry for current version number", "NEWS file does not contains entry for current version number")},
          if(values$has_bug_reports[2] == -1){"Metric is not applicable for this source of package"}
            else{ ifelse(values$has_bug_reports[1] == 1, paste("Bug reports URL:", values$has_bug_reports[2]), "The Bugs are not publicly documented")},
          if(values$status_of_last_30_reported_bugs[2] == -1){"Metric is not applicable for this source of package"}
            else{"Percentage of last 30 bugs closed"},
          if(values$exported_objects_with_documentation[2] == -1){"Metric is not applicable for this source of package"}
            else{"Proportion of exported objects documented"},
          if(values$source_code_is_public[2] == -1){"Metric is not applicable for this soucre of package"}
            else{ ifelse(values$source_code_is_public[1] == 1, paste("Source code URL:", values$source_code_is_public[2]), "Package does not have a Source code URL")},
          if(values$has_a_package_maintainer[2] == -1){"Metric is not applicable for this soucre of package"}
              else{ ifelse(values$has_a_package_maintainer[1] == 1, values$has_a_package_maintainer[2], "Package does not have a Maintainer")}
)
table_infobox<-data.frame(Metric,Result,Detail)

knitr::kable(table_infobox, format='pandoc')

```

### Comments for Maintenance Metrics(`r nrow(comment_mm2)`):

```{r echo=FALSE}
comment_mm2 <- data.frame(comment_mm2 %>% map(rev))
    
table_mm<-data.frame("User ID"=comment_mm2$user_name,"Role"= comment_mm2$user_role, "Time"= comment_mm2$added_on,"Comments"=comment_mm2$comment)
  knitr::kable(table_mm, format='pandoc')

```


## Community Usage Metrics

```{r echo=FALSE}

Metric<-c("Package Maturity","Version Maturity")

Result<-c(
     if(values$time_since_first_release_info == -1){"NA"}
      else{values$time_since_first_release_info},
     if(values$time_since_version_release_info == -1){"NA"}
      else{values$time_since_version_release_info}
)

Detail<-c(
     if(values$time_since_first_release_info == -1){"Metric is not applicable for this source of package"}
       else{"Months since first release."},
     if(values$time_since_version_release_info == -1){"Metric is not applicable for this source of package"}
       else{"Months since version release."}
)

table_infobox_cum<-data.frame(Metric,Result,Detail)

knitr::kable(table_infobox_cum, format='pandoc')

if (riskmetrics_cum$no_of_downloads_last_year[1] != "NA") {
    hc <- highchart() %>%
      hc_xAxis(categories = riskmetrics_cum$month) %>%
      hc_xAxis(
        title = list(text = "Months"),
        plotLines = list(
          list(
            label = list(text = riskmetrics_cum$ver_release[1]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[1]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[2]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[2]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[3]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[3]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[4]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[4]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[5]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[5]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[6]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[6]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[7]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[7]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[8]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[8]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[9]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[9]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[10]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[10]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[11]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[11]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[12]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[12]
          )
        )
      ) %>%
      hc_add_series(
        name = params$package,
        data = riskmetrics_cum$no_of_downloads,
        color = "blue"
      ) %>%
      hc_yAxis(title = list(text = "Downloads")) %>%
      hc_title(text = "Number of Downloads") %>%
      hc_subtitle(
        text = paste(
          "Total Number of Downloads :",
          sum(riskmetrics_cum$no_of_downloads)
        ),
        align = "right",
        style = list(color = "#2b908f", fontWeight = "bold")
      ) %>%
      hc_add_theme(hc_theme_elementary())
  } else{
    hc <- highchart() %>%
      hc_xAxis(categories = NULL) %>%
      hc_xAxis(title = list(text = "Months")) %>%
      hc_add_series(name = params$package, data = NULL) %>%
      hc_yAxis(title = list(text = "Downloads")) %>%
      hc_title(text = "NUMBER OF DOWNLOADS IN THE PAST YEAR") %>%
      hc_subtitle(
        text = paste("Number of Downloads in the past year not found"),
        style = list(color = "#f44336", fontWeight = "bold")
      ) %>%
      hc_add_theme(hc_theme_elementary())
  }
hc

```

### Comments for Community Usage Metrics(`r nrow(comment_cum2)`):

```{r echo=FALSE}
comment_cum2 <- data.frame(comment_cum2 %>% map(rev))
  
table_cum<-data.frame("User ID"=comment_cum2$user_name,"Role"= comment_cum2$user_role, "Time"= comment_cum2$added_on,"Comments"=comment_cum2$comment)
  knitr::kable(table_cum, format='pandoc')
  
```


## Testing Metrics


```{r echo=FALSE}
  bands = data.frame(
    start = c(0, 40, 80),
    end = c(40, 80, 100),
    color = ifelse(values$riskmetrics_tm[2] != -1, c("#ea3838", "#ffac29", "#00CC00"), c("#808080", "#808080", "#808080")),
    stringsAsFactors = FALSE
  )
  bands2 = data.frame(
    start = c(0, 40, 80),
    end = c(40, 80, 100),
    color = ifelse(values$riskmetrics_tm[2] != -1, c("#ea3838", "#ffac29", "#00CC00"), c("#808080", "#808080", "#808080")),
    stringsAsFactors = FALSE
  )
  amAngularGauge(
    x = as.numeric(values$riskmetrics_tm[1]),
    start = 0,
    end = 100,
    bands = bands,
    secondAxe = TRUE,
    start2 = 0,
    end2 = 100,
    bands2 = bands2
  )
```


### Comments for Testing Metrics(`r nrow(comment_tm2)`):


```{r echo=FALSE}
    comment_tm2 <- data.frame(comment_tm2 %>% map(rev))
    
table_tm<-data.frame("User ID"=comment_tm2$user_name,"Role"= comment_tm2$user_role, "Time"= comment_tm2$added_on,"Comments"=comment_tm2$comment)
  knitr::kable(table_tm, format='pandoc')


```






