---
title:   "<span style='color: steelblue;'>R Package Risk Assessment </span>"
subtitle: "R Validation Hub"
author: "<br><span style='font-weight:bold'>Author (Role): </span> `r input$name` (`r input$role `)"
date: "<span style='font-weight:bold'>Report Date: </span>`r format(Sys.time(), '%B %d, %Y')`"
always_allow_html: true
output: html_document
runtime: shiny
params:
  package: NA
  version: NA
  cwd: NA
---


```{r  echo=FALSE,warning=FALSE }

setwd(params$cwd)

pkg_GenInfo = db_fun(paste0(
  "SELECT * FROM package WHERE name ='",
  params$package,
  "'"
))

comment_o <-
  db_fun(
    paste0(
      "SELECT * FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'o'"
    )
  )

  riskmetrics_mm <-
    db_fun(
      paste0(
        "SELECT * FROM MaintenanceMetrics WHERE MaintenanceMetrics.mm_id ='",
        params$package,
        "'"
      )
    )
   
  has_vignettes <- c(strsplit(riskmetrics_mm$has_vignettes,",")[[1]][1], strsplit(riskmetrics_mm$has_vignettes,",")[[1]][2])
  has_website <- c(strsplit(riskmetrics_mm$has_website,",")[[1]][1], strsplit(riskmetrics_mm$has_website,",")[[1]][2])
  has_news <- c(strsplit(riskmetrics_mm$has_news,",")[[1]][1], strsplit(riskmetrics_mm$has_news,",")[[1]][2])
  news_current <- c(strsplit(riskmetrics_mm$news_current,",")[[1]][1], strsplit(riskmetrics_mm$news_current,",")[[1]][2])
  has_bug_reports_url <- c(strsplit(riskmetrics_mm$has_bug_reports_url,",")[[1]][1], strsplit(riskmetrics_mm$has_bug_reports_url,",")[[1]][2])
  bugs_status <- c(strsplit(riskmetrics_mm$bugs_status,",")[[1]][1], strsplit(riskmetrics_mm$bugs_status,",")[[1]][2])
  export_help <- c(strsplit(riskmetrics_mm$export_help,",")[[1]][1], strsplit(riskmetrics_mm$export_help,",")[[1]][2])
  has_source_control <- c(strsplit(riskmetrics_mm$has_source_control,",")[[1]][1], strsplit(riskmetrics_mm$has_source_control,",")[[1]][2])
  has_maintainer <- c(strsplit(riskmetrics_mm$has_maintainer,",")[[1]][1], strsplit(riskmetrics_mm$has_maintainer,",")[[1]][2])

  riskmetrics_cum <-
    db_fun(
      paste0(
        "SELECT * FROM CommunityUsageMetrics WHERE cum_id ='",
        params$package,
        "'"
      )
    )
 
  pkgs_in_db <- db_fun(paste0("SELECT cum_id FROM CommunityUsageMetrics"))
  
  if (!(params$package %in% pkgs_in_db$cum_id)) {
    metric_cum_Info_upload_to_DB(params$package)
    riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
  } else{
    riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
  }
   
  time_since_first_release_info <- riskmetrics_cum$time_since_first_release[1] 
  time_since_version_release_info <- riskmetrics_cum$time_since_version_release[1]
  no_of_downloads_last_year_info <-
        riskmetrics_cum$no_of_downloads_last_year[1]
  

  package_id <- db_fun(paste0("SELECT id FROM package WHERE name = ", "'", input$select_pack, "'", ";"))
  metric_id <- db_fun(paste0("SELECT id FROM metric WHERE name = 'covr_coverage';"))
  covr_coverage <- db_fun(
    paste0("SELECT value FROM package_metrics WHERE ",
           "package_id = ", package_id,
           " AND ",
           "metric_id = ", metric_id,
           ";"
    )
  )
  covr_coverage <- covr_coverage$value
  

   comment_mm <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'mm'"
        )
      )  
 
   comment_cum <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'cum'"
        )
      )

    comment_tm <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'tm'"
        )
      )
 
```


<div class="heading_report"> Report of the "`r pkg_GenInfo$name`" Package:</div>

<div class="report">This **`r pkg_GenInfo$name`** package report was generated using  **`r params$version`** riskmetric version. Metrics were reviewed via the R Package Risk Assessment Application.</div>



```{r setup, include=FALSE}
library(knitr)
library(shiny)
library(shinyjs)

knitr::opts_chunk$set(echo = F,fig.width=5.5, fig.height=3.4)

#Plot parameters
#define base_size of text
bsize_text <- 11

#define background color of plots
p_color <- 'white'

```


<hr style="
  height: 2px;
  border: none;
  color: #3c8dbc;
  background-color: #3c8dbc">

<div class="blue para-header">Summary</div>

**Score:** `r pkg_GenInfo$score`
```{r echo=FALSE}
 if (!identical(pkg_GenInfo$decision, character(0)) && pkg_GenInfo$decision != "") {
    HTML(paste("<br>", "<h5>Overall risk: ", "<b>", pkg_GenInfo$decision, "</b></h5>"))
  } else{
    HTML(paste("<br>", "<h5><b>Overall risk: Pending</b></h5>"))
  }
```

**Overall Comments(`r nrow(comment_o)`):**
<div class="col-md-12 comments-box">

```{r echo=FALSE}

  comment_o <- data.frame(comment_o %>% map(rev))
   HTML(paste(
      "<div class='col-sm-12 comment-border-bottom'><i class='fa fa-user-tie fa-2x d-inline'></i><h3 class='ml-3 d-inline'><b class='user-name-color'>",
      comment_o$user_name,
      "(",
      comment_o$user_role,
      ")",
      "</b><sub>",
      comment_o$added_on,
      "</sub></h3><h4 class='ml-3 lh-4'>",
      comment_o$comment,
      "</h4></div>"
    ))
```
</div>
<div class="blue para-header">General Info</div>

**Package:** `r pkg_GenInfo$name`

**Version:** `r pkg_GenInfo$version`

**Title:** `r pkg_GenInfo$title`

**Description:** `r pkg_GenInfo$description`

**Author:** `r pkg_GenInfo$author`

**Maintainer:** `r pkg_GenInfo$maintainer`

**License:** `r pkg_GenInfo$license`

**Published:** `r pkg_GenInfo$published`

<div class="blue para-header mb-4">Maintenance Metrics</div>

```{r echo=FALSE, results="asis"}
div(
class = "row mb-3",
  infoBox(
    title = "Presence of vignettes?",
    if(has_vignettes[1] == 1){"YES"}
    else if(has_vignettes[2] == -1){"NA"}
    else{"NO"},
    width = 3,
    if(has_vignettes[2] == -1){"Metric is not applicable for this source of package"}
    else{paste("The package has", has_vignettes[2], "Vignettes")},
    icon = icon(
      ifelse(has_vignettes[1] == 1, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(has_vignettes[1] == 1, "green", "red"),
    fill = TRUE
  ),
  infoBox(
    title = "Associated website URL?",
    if(has_website[1] == 1){"YES"}
    else if(has_website[2] == -1){"NA"}
    else{"NO"},
    width = 3,
    if(has_website[2] == -1){"Metric is not applicable for this source of package"}
    else{ ifelse(has_website[1] == 1, paste("Website:",has_website[2]), "The package does not have an associated website URL")},
    icon = icon(
      ifelse(has_website[1] == 1, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(has_website[1] == 1, "green", "red"),
    fill = TRUE
  ),
  infoBox(
    title = "NEWS?",
    if(has_news[1] == 1){"YES"}
    else if(has_news[2] == -1){"NA"}
    else{"NO"},
    width = 3,
    if(has_news[2] == -1){"Metric is not applicable for this source of package"}
    else{ ifelse(has_news[1] == 1, "The package has a NEWS file.", "The package does not have a NEWS file")},
    icon = icon(
      ifelse(has_news[1] == 1, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(has_news[1] == 1, "green", "red"),
    fill = TRUE
  )
)
```

```{r echo=FALSE}
div(
class = "row mb-3",
  infoBox(
    title = "News is current?",
    if(news_current[1] == 1){"YES"}
    else if(news_current[2] == -1){"NA"}
    else{"NO"},
    width = 3,
    if(news_current[2] == -1){"Metric is not applicable for this source of package"}
    else{ ifelse(news_current[1] == 1, "NEWS file contains entry for current version number", "NEWS file does not contains entry for current version number")},
    icon = icon(
      ifelse(news_current[1] == 1, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(news_current[1] == 1, "green", "red"),
    fill = TRUE
  ),
  infoBox(
    title = "Bugs publicly documented?",
    if(has_bug_reports_url[1] == 1){"YES"}
    else if(has_bug_reports_url[2] == -1){"NA"}
    else{"NO"},
    width = 3,
    if(has_bug_reports_url[2] == -1){"Metric is not applicable for this source of package"}
    else{ ifelse(has_bug_reports_url[1] == 1, paste("Bug reports URL:", has_bug_reports_url[2]), "The Bugs are not publicly documented")},
    icon = icon(
      ifelse(has_bug_reports_url[1] == 1, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(has_bug_reports_url[1] == 1, "green", "red"),
    fill = TRUE
  ),
  infoBox(
    title = "Bug closure",
    if(bugs_status[2] == -1){"NA"}
    else{paste0(bugs_status[1],"%")},
    subtitle = if(bugs_status[2] == -1){"Metric is not applicable for this source of package"}
    else{"Percentage of last 30 bugs closed"},
    width = 3,
    fill = TRUE
  )
)
```    

```{r echo= FALSE}
div(
  class = "row mb-3",
  infoBox(
    title = "Documentation",
    if(export_help[2] == -1){"NA"}
    else{paste0(export_help[1],"%")},
    subtitle = if(export_help[2] == -1){"Metric is not applicable for this source of package"}
    else{"Proportion of exported objects documented"},
    width = 3,
    fill = TRUE
  ),
  infoBox(
    title = "Source code public?",
    if(has_source_control[1] == 1){"YES"}
    else if(has_source_control[2] == -1){"NA"}
    else{"NO"},
    width = 3,
    if(has_source_control[2] == -1){"Metric is not applicable for this soucre of package"}
    else{ ifelse(has_source_control[1] == 1, paste("Source code URL:", has_source_control[2]), "Package does not have a Source code URL")},
    icon = icon(
      ifelse(has_source_control[1] == 1, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(has_source_control[1] == 1, "green", "red"),
    fill = TRUE
  ),
  infoBox(
    title = "Has a maintainer?",
    if(has_maintainer[1] == 1){"YES"}
    else if(has_maintainer[2] == -1){"NA"}
    else{"NO"},
    width = 3,
    if(has_maintainer[2] == -1){"Metric is not applicable for this soucre of package"}
    else{ ifelse(has_maintainer[1] == 1, has_maintainer[2], "Package does not have a Maintainer")},
    icon = icon(
      ifelse(
        has_maintainer[1] == 1, "thumbs-up", "thumbs-down"),
        lib = "glyphicon"
    ),
    color = ifelse(has_maintainer[1] == 1, "green", "red"),
    fill = TRUE
  )
)

```

<div class="row col-md-12 comments">Comments for Maintenance Metrics(`r nrow(comment_mm)`):</div>
<div class="col-md-12 comments-box">

```{r echo=FALSE}
comment_mm <- data.frame(comment_mm %>% map(rev))
    HTML(paste(
      "<div class='col-sm-12 comment-border-bottom single-comment-div'><i class='fa fa-user-tie fa-2x d-inline'></i><h3 class='ml-3 d-inline'><b class='user-name-color'>",
      comment_mm$user_name,
      "(",
      comment_mm$user_role,
      ")",
      "</b><sub>",
      comment_mm$added_on,
      "</sub></h3><h4 class='ml-3 lh-4'>",
      comment_mm$comment,
      "</h4></div>"
 ))

```

</div>
<div class="row col-md-12 blue mb-4 para-header">Community Usage Metrics</div>

```{r echo=FALSE}
  
  infoBox(
    title = "Package Maturity",
    time_since_first_release_info,
    subtitle = ifelse(time_since_first_release_info != "NA",
                      "Months since first release.",
                      "Metric is not applicable for this source of package."),
    icon = shiny::icon("calendar"),
    width = 3,
    fill = TRUE
  )

  infoBox(
    title = "Version Maturity",
    time_since_version_release_info,
    subtitle = ifelse(time_since_version_release_info != "NA", 
                      "Months since version release.",
                      "Metric is not applicable for this source of package."),
    icon = shiny::icon("calendar"),
    width = 3,
    fill = TRUE
  )
  
  infoBox(
    title = "Download Count",
    formatC(no_of_downloads_last_year_info, format="f", big.mark=",", digits=0),
    subtitle = ifelse(no_of_downloads_last_year_info != "NA", 
                      "Downloads in Last Year",
                      "Metric is not applicable for this source of package."),
    icon = shiny::icon("signal"),
    width = 3,
    fill = TRUE
  )
  


```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

```{r echo=FALSE}
p <- num_dwnlds_plot(data = riskmetrics_cum,
                    input_select_pack = params$package)
tagList(p)
```

```{r echo=FALSE}

tags$script(HTML("setTimeout(function(){
var element = document.querySelectorAll('.info-box-content');
for (var i = 0; i < element.length; i++) {
	if(element[i].innerText.indexOf('NA') > -1) {
		var iconEle = element[i].previousElementSibling
		iconEle.firstElementChild.style.background = 'grey';
        var icn = iconEle.firstElementChild;
        if(icn.classList.toString().indexOf('fa-calendar') > -1 || icn.classList.toString().indexOf('fa-bar-chart')> -1){
            
        } else {
            icn.classList.add('icon-color-grey');
        }
	}}
},500)" )) 

if (riskmetrics_cum$no_of_downloads_last_year[1] == 0) {
  tags$script(
    HTML(
      "setTimeout(function(){
         var element = document.getElementsByClassName('highcharts-container ')[0].getElementsByClassName('highcharts-subtitle');
        element[0].style.fontSize = '16px';
        var xVal = element[0]['x'].baseVal[0].value;
        element[0]['y'].baseVal[0].value = xVal/2;
      },500)"
    )
  )
}
```

<div class="row col-md-12 comments">Comments for Community Usage Metrics(`r nrow(comment_cum)`):</div>
<div class="col-md-12 comments-box">

```{r echo=FALSE}
comment_cum <- data.frame(comment_cum %>% map(rev))
   HTML(paste(
      "<div class='col-sm-12 comment-border-bottom'><i class='fa fa-user-tie fa-2x d-inline'></i><h3 class='ml-3 d-inline'><b class='user-name-color'>",
      comment_cum$user_name,
      "(",
      comment_cum$user_role,
      ")",
      "</b><sub>",
      comment_cum$added_on,
      "</sub></h3><h4 class='ml-3 lh-4'>",
      comment_cum$comment,
      "</h4></div>"
    ))
```

</div>
<div class="blue para-header">Testing Metrics</div>

<br>

```{r echo=FALSE}

  bands = data.frame(
    start = c(0, 40, 80),
    end = c(40, 80, 100),
    color = ifelse(covr_coverage != "pkg_metric_error",
                   c("#ea3838", "#ffac29", "#00CC00"),
                   c("#808080", "#808080", "#808080")),
    stringsAsFactors = FALSE
  )
  bands2 = data.frame(
    start = c(0, 40, 80),
    end = c(40, 80, 100),
    color = ifelse(covr_coverage != "pkg_metric_error",
                   c("#ea3838", "#ffac29", "#00CC00"),
                   c("#808080", "#808080", "#808080")),
    stringsAsFactors = FALSE
  )
  amAngularGauge(
    x = as.numeric(ifelse(covr_coverage == "NA", 0, covr_coverage)),
    start = 0,
    end = 100,
    bands = bands,
    secondAxe = TRUE,
    start2 = 0,
    end2 = 100,
    bands2 = bands2
  )
```

```{r echo=FALSE}

if(covr_coverage == "pkg_metric_error"){
  tags$script(HTML(
  "
  setTimeout(function() {
    var elementCircle = document.getElementsByClassName('ramcharts_base')[0].getElementsByTagName('circle')[0];
    elementCircle.nextSibling.remove();
    elementCircle.remove();
    var element = document.getElementsByClassName('ramcharts_base')[0].getElementsByTagName('svg')[0];
    var textElement = document.createElementNS('http://www.w3.org/2000/svg', 'text');
    textElement.setAttributeNS(null, 'x', element.width.baseVal.value/2);
    textElement.setAttributeNS(null, 'y', element.height.baseVal.value/2 +20);
    textElement.setAttributeNS(null,'font-size','20');
    textElement.setAttributeNS(null,'fill','red');
    textElement.setAttributeNS(null,'text-anchor','middle');
    textElement.setAttributeNS(null,'class','gauge-error-text');
    var txt = document.createTextNode('Metric is not applicable');
    textElement.appendChild(txt);
    element.appendChild(textElement);
    
    var textElement2 = document.createElementNS('http://www.w3.org/2000/svg', 'text');
    textElement2.setAttributeNS(null, 'x', element.width.baseVal.value/2);
    textElement2.setAttributeNS(null, 'y', element.height.baseVal.value/2 +50);
    textElement2.setAttributeNS(null,'font-size','20');
    textElement2.setAttributeNS(null,'fill','red');
    textElement2.setAttributeNS(null,'text-anchor','middle');
    textElement2.setAttributeNS(null,'class','gauge-error-text');
    var txt2 = document.createTextNode('for this source of package');
    textElement2.appendChild(txt2);
    element.appendChild(textElement2);
    var allEle = element.querySelectorAll('text')
    for(let i=0; i<allEle.length; i++){
      if(allEle[i].textContent == 100 && allEle[i+1].textContent == 0){
          allEle[i+1].textContent = 'NA';
      }
    }
  }, 1000)
  "
  ))
}
```

<br>
<div class="row col-md-12 comments">Comments for Testing Metrics(`r nrow(comment_tm)`):</div>

<style>
.user-name-color {
color: #7f7f7f;
}
.ml-3 {
    margin-left: 1rem!important;
    font-size: 17px;
}
.comment-border-bottom {
  padding:0px;
  border-bottom: 1px solid rgba(0,0,0,.125);
  margin-bottom: 2rem;
}

.fa-user-tie {
  color: rgba(77,141,201,.70);
  top: 35%;
  left: 0px;
}

.blue {
    color: steelblue;
    font-size: 30px;
}
.comments{
  color:steelblue;
  font-size:22px;
  margin-top: 2rem;
}
.report{
font-size:14px
color: steelblue;
}
.heading_report {
    font-size: 23px;
    font-weight: bold;
    
}
.d-inline {
  display: inline;
}

.info-box-content, .info-box-icon {
  display: inline;
}

.glyphicon-thumbs-up {
  background: green;
  color: #fff;
  padding: 3px;
}

.glyphicon-thumbs-down {
  background: red;
  color: #fff;
  padding: 3px;
}

.fa-bar-chart, .fa-calendar {
  background: deepskyblue;
  color: #fff;
  padding: 3px;
}
.mb-3 {
  margin-bottom: 1rem;
}
.mb-4 {
  margin-bottom: 1.5rem;
}

.comments-box {
  max-height: 300px;
  overflow-y: auto;
  padding: 10px;
  border: 1px solid rgb(0, 0, 0.125);
  margin-bottom: 2rem;
}
.amcharts-chart-div > a {
  display: none !important;
}
.info-box-number {
  font-weight: bold;
}
.title.toc-ignore {
  text-align: center;
}
.para-header{
  text-align: left;
  text-decoration: none;
  text-underline-position: under;
}

.highcharts-container {
  margin-top: 3rem;
}

.icon-color-grey::before {
  color: grey;
}

</style>

<div class="col-md-12 comments-box">

```{r echo=FALSE}
    comment_tm <- data.frame(comment_tm %>% map(rev))
    HTML(paste(
      "<div class='col-sm-12 comment-border-bottom'><i class='fa fa-user-tie fa-2x d-inline'></i><h3 class='ml-3 d-inline'><b class='user-name-color'>",
      comment_tm$user_name,
      "(",
      comment_tm$user_role,
      ")",
      "</b><sub>",
      comment_tm$added_on,
      "</sub></h3><h4 class='ml-3 lh-4'>",
      comment_tm$comment,
      "</h4></div>"
    ))

```
</div>

