---
title: "R Package Risk Assessment"
subtitle: "R Validation Hub"
author: "<br><span style='font-weight:bold'>Author: </span>GSK"
date: "<span style='font-weight:bold'>Report Date: </span>`r format(Sys.time(), '%B %d, %Y')`"
always_allow_html: true
output: pdf_document
params:
  package: NA
  cwd: NA
---


```{r  echo=FALSE,warning=FALSE}
setwd(params$cwd)

res4 <- db_fun(paste0(
  "SELECT * FROM Packageinfo WHERE package ='",
  params$package,
  "'"
))
riskmetrics_tm <-
    db_fun(
      paste0(
        "SELECT * FROM TestMetrics WHERE TestMetrics.tm_id ='",
        params$package,
        "'"
      )
    )
 riskmetrics_cum <-
    db_fun(
      paste0(
        "SELECT * FROM CommunityUsageMetrics WHERE cum_id ='",
        params$package,
        "'"
      )
    )

riskmetrics_infotimesince <-
    db_fun(
      paste0(
        "SELECT * FROM CommunityUsageMetrics WHERE cum_id ='",
        params$package,
        "'"
      )
    )
  # Load the data table column into reactive variable for time sice first release.
  time_since_first_release_info <- riskmetrics_infotimesince$time_since_first_release[1] 
  time_since_version_release_info <-riskmetrics_infotimesince$time_since_version_release[1]
  riskmetrics_mm <-
    db_fun(
      paste(
        "SELECT * FROM MaintenanceMetrics WHERE MaintenanceMetrics.mm_id ='",
        params$package,
        "'",
        sep = ""
      )
    )
   
 values$package_has_vignettes <- riskmetrics_mm$package_has_vignettes
  values$package_has_website <- riskmetrics_mm$package_has_website
  values$package_has_news <- riskmetrics_mm$package_has_news
  values$news_is_current <- riskmetrics_mm$news_is_current
  values$has_bug_reports <- riskmetrics_mm$has_bug_reports
  values$status_of_last_30_reported_bugs <-
    riskmetrics_mm$status_of_last_30_reported_bugs
  values$exported_objects_with_documentation <-
    riskmetrics_mm$exported_objects_with_documentation
  values$source_code_is_public <- riskmetrics_mm$source_code_is_public
  values$has_a_package_maintainer <-
    riskmetrics_mm$has_a_package_maintainer 
  
 comment_mm2 <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'mm'"
        )
      )  
  
```

### Report of the " `r res4$package` " Package

Write exmaple paragraph for this document When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks.

```{r setup, include=FALSE}

knitr::opts_chunk$set(fig.width=5.5, fig.height=3.4)

#Plot parameters
#define base_size of text
bsize_text <- 11

#define background color of plots
p_color <- 'white'

```


<hr style="
  height: 2px;
  border: none;
  color: #000000;
  background-color: #000000">

## General Info

**Package:** `r res4$package`

**Version:** `r res4$version`

**Title:** `r res4$title`

**Description:** `r res4$description`

**Author:** `r res4$author`

**Maintainer:** `r res4$maintainer`

**License:** `r res4$license`

**Published:** `r res4$published`

**Decision:** `r res4$decision`

**Overall Comment:**   

```{r, echo = FALSE}

    # comment_o <-
    #   db_fun(
    #     paste0(
    #       "SELECT * FROM Comments WHERE comm_id = '",
    #       params$package,
    #       "' AND comment_type = 'o'"
    #     )
    #   )
    # comment_o <- data.frame(comment_o %>% map(rev))
    # paste(
    #   "<div class='col-sm-12 comment-border-bottom'><i class='fa fa-user-tie fa-4x'></i><h3 class='ml-3'><b class='user-name-color'>",
    #   "<h3>",
    #   comment_o$user_name,
    #   "(",
    #   comment_o$user_role,
    #   ")",
    #   "</b><sub>",
    #   comment_o$added_on,
    #   "</sub></h3><h4>",
    #   comment_o$comment,
    #   "</h4>"
    # )

```


<br>

## Maintenance Metrics

```{r echo=FALSE}
 
infoBox(
    title = "Vignette",
    ifelse(values$package_has_vignettes == 1, "YES", "NO"),
    width = 3,
    subtitle = "It is good practice to provide additional help documentation in the form of vignettes",
    icon = icon(
      ifelse(values$package_has_vignettes, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(values$package_has_vignettes, "green", "red"),
    fill = TRUE
  )
  infoBox(
    title = "Package has website",
    ifelse(values$package_has_website == 1, "YES", "NO"),
    width = 3,
    subtitle = "It is good practice to maintain a website with further supporting information",
    icon = icon(
      ifelse(values$package_has_website, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(values$package_has_website, "green", "red"),
    fill = TRUE
  )
  
  infoBox(
    title = "Has News?",
    ifelse(values$package_has_news == 1, "YES", "NO"),
    width = 3,
    subtitle = "A news feed makes users aware of updates to the package and highlights the areas of greatest risk",
    icon = icon(
      ifelse(values$package_has_news, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(values$package_has_news, "green", "red"),
    fill = TRUE
  )
    infoBox(
    title = "News is Current?",
    ifelse(values$news_is_current == 1, "YES", "NO"),
    width = 3,
    subtitle = "If it is not current, there is a risk that users do not use the package in a way of author/maintainer intends",
    icon = icon(
      ifelse(values$news_is_current, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(values$news_is_current, "green", "red"),
    fill = TRUE
  )
    
    infoBox(
    title = "Does the package have Bug Report?",
    ifelse(values$has_bug_reports == 1, "YES", "NO"),
    width = 3,
    subtitle = "Bugs can be logged by emails, but the better practice is to provide a formal mechanism for bug tracking",
    icon = icon(
      ifelse(values$has_bug_reports, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(values$has_bug_reports, "green", "red"),
    fill = TRUE
  )
    infoBox(
    title = "Bugs Status",
    values$status_of_last_30_reported_bugs,
    subtitle = "The higher the percentage of closed bugs/issues, the better",
    width = 3,
    fill = TRUE
  )
    
  infoBox(
    title = "Export Help",
    values$exported_objects_with_documentation,
    subtitle = "Higher percentages indicate better documentation coverage",
    width = 3,
    fill = TRUE
  )  
  
  infoBox(
    title = "Source code is public?",
    ifelse(values$source_code_is_public == 1, "YES", "NO"),
    width = 3,
    subtitle = "The use of source control is good practice that facilitates development",
    icon = icon(
      ifelse(values$source_code_is_public, "thumbs-up", "thumbs-down"),
      lib = "glyphicon"
    ),
    color = ifelse(values$source_code_is_public, "green", "red"),
    fill = TRUE
  )
  
  infoBox(
    title = "Has a package maintainer?",
    ifelse(values$has_a_package_maintainer == 1, "YES", "NO"),
    width = 3,
    subtitle = "Package should be actively maintained to ensure it meets current standards as it presents a risk",
    icon = icon(
      ifelse(
        values$has_a_package_maintainer,
        "thumbs-up",
        "thumbs-down"
      ),
      lib = "glyphicon"
    ),
    color = ifelse(values$has_a_package_maintainer, "green", "red"),
    fill = TRUE
  )
  
  
```

<br>

```{r echo=FALSE }
    # comment_mm2 <- data.frame(comment_mm2 %>% map(rev))
    # req(comment_mm2$comment)
    # values$mm_comment_submitted <- "no"
    # paste("<div class='col-sm-12 comment-border-bottom single-comment-div'><i class='fa fa-user-tie fa-4x'></i><h3 class='ml-3'><b   
    #       class='user-name-color'>",comment_mm2$user_name, "(",comment_mm2$user_role,")", "</b><sub>", comment_mm2$added_on,"</sub></h3><h4
    #       class='ml-3 lh-4'>", comment_mm2$comment,"</h4></div>")

```

<br>

## Community Usage Metrics

<br>

```{r echo=FALSE}
  
  infoBox(
    title = "Time Since First Release?",
    time_since_first_release_info,
    subtitle = "The longer a package has been in existence, the more exposure it has had to community testing",
    icon = shiny::icon("calendar"),
    width = 3,
    fill = TRUE
  )

  infoBox(
    title = "Time Since Version Release?",
    time_since_version_release_info,
    subtitle = "The more recent a version, the less exposure it has had to community testing",
    icon = shiny::icon("calendar"),
    width = 3,
    fill = TRUE
  )
  
  infoBox(
    title = "Total number of downloads last year",
    sum(riskmetrics_cum$no_of_downloads),
    width = 3,
    fill = TRUE
  )
  
if (riskmetrics_cum$no_of_downloads[1] != "NA") {
    hc <- highchart() %>%
      hc_xAxis(categories = riskmetrics_cum$month) %>%
      hc_xAxis(
        title = list(text = "Months"),
        plotLines = list(
          list(
            label = list(text = riskmetrics_cum$ver_release[1]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[1]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[2]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[2]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[3]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[3]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[4]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[4]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[5]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[5]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[6]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[6]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[7]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[7]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[8]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[8]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[9]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[9]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[10]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[10]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[11]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[11]
          ),
          list(
            label = list(text = riskmetrics_cum$ver_release[12]),
            color = "#FF0000",
            width = 2,
            value = riskmetrics_cum$position[12]
          )
        )
      ) %>%
      hc_add_series(
        name = params$package,
        data = riskmetrics_cum$no_of_downloads,
        color = "blue"
      ) %>%
      hc_yAxis(title = list(text = "Downloads")) %>%
      hc_title(text = "Number of Downloads") %>%
      hc_subtitle(
        text = paste(
          "Total Number of Downloads :",
          sum(riskmetrics_cum$no_of_downloads)
        ),
        align = "right",
        style = list(color = "#2b908f", fontWeight = "bold")
      ) %>%
      hc_add_theme(hc_theme_elementary())
  } else{
    hc <- highchart() %>%
      hc_xAxis(categories = NULL) %>%
      hc_xAxis(title = list(text = "Months")) %>%
      hc_add_series(name = params$package, data = NULL) %>%
      hc_yAxis(title = list(text = "Downloads")) %>%
      hc_title(text = "Number of Downloads") %>%
      hc_subtitle(
        text = paste("Number of Downloads in last one year not found"),
        style = list(color = "#f44336", fontWeight = "bold")
      ) %>%
      hc_add_theme(hc_theme_elementary())
  }
hc

```

<br>

## Testing Metrics
```{r echo=FALSE}

  infoBox(
    title = "Test Coverage",
    riskmetrics_tm$test_coverage,
    width = 3,
    fill = TRUE
  )

bands = data.frame(
    start = c(0, 40, 80),
    end = c(40, 80, 100),
    color = c("#ea3838", "#ffac29", "#00CC00"),
    stringsAsFactors = FALSE
  )
  bands2 = data.frame(
    start = c(0, 40, 80),
    end = c(40, 80, 100),
    color = c("#ea3838", "#ffac29", "#00CC00"),
    stringsAsFactors = FALSE
  )
  amAngularGauge(
    x = riskmetrics_tm$test_coverage,
    start = 0,
    end = 100,
    bands = bands,
    secondAxe = TRUE,
    start2 = 0,
    end2 = 100,
    bands2 = bands2
  )
```

 



