---
title: '<span style=''color: steelblue;''>R Package Risk Assessment </span>'
author: '**Author (Role): `r input$name` (`r input$role `)**'
date: "**Report Date: `r format(Sys.time(), '%B %d, %Y')`**"
output:
  word_document
params:
  cwd: NA
  package: NA
  version: NA
subtitle: R Validation Hub
always_allow_html: yes
---


```{r  echo=FALSE,warning=FALSE }

setwd(params$cwd)

pkg_GenInfo = db_fun(paste0(
  "SELECT * FROM Packageinfo WHERE package ='",
  params$package,
  "'"
))

comment_o <-
  db_fun(
    paste0(
      "SELECT * FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'o'"
    )
  )

  riskmetrics_mm <-
    db_fun(
      paste0(
        "SELECT * FROM MaintenanceMetrics WHERE MaintenanceMetrics.mm_id ='",
        params$package,
        "'"
      )
    )
   
  package_has_vignettes <- c(strsplit(riskmetrics_mm$package_has_vignettes,",")[[1]][1], strsplit(riskmetrics_mm$package_has_vignettes,",")[[1]][2])
  package_has_website <- c(strsplit(riskmetrics_mm$package_has_website,",")[[1]][1], strsplit(riskmetrics_mm$package_has_website,",")[[1]][2])
  package_has_news <- c(strsplit(riskmetrics_mm$package_has_news,",")[[1]][1], strsplit(riskmetrics_mm$package_has_news,",")[[1]][2])
  news_is_current <- c(strsplit(riskmetrics_mm$news_is_current,",")[[1]][1], strsplit(riskmetrics_mm$news_is_current,",")[[1]][2])
  has_bug_reports <- c(strsplit(riskmetrics_mm$has_bug_reports,",")[[1]][1], strsplit(riskmetrics_mm$has_bug_reports,",")[[1]][2])
  status_of_last_30_reported_bugs <- c(strsplit(riskmetrics_mm$status_of_last_30_reported_bugs,",")[[1]][1], strsplit(riskmetrics_mm$status_of_last_30_reported_bugs,",")[[1]][2])
  exported_objects_with_documentation <- c(strsplit(riskmetrics_mm$exported_objects_with_documentation,",")[[1]][1], strsplit(riskmetrics_mm$exported_objects_with_documentation,",")[[1]][2])
  source_code_is_public <- c(strsplit(riskmetrics_mm$source_code_is_public,",")[[1]][1], strsplit(riskmetrics_mm$source_code_is_public,",")[[1]][2])
  has_a_package_maintainer <- c(strsplit(riskmetrics_mm$has_a_package_maintainer,",")[[1]][1], strsplit(riskmetrics_mm$has_a_package_maintainer,",")[[1]][2])

  riskmetrics_cum <-
    db_fun(
      paste0(
        "SELECT * FROM CommunityUsageMetrics WHERE cum_id ='",
        params$package,
        "'"
      )
    )
 
  pkgs_in_db <- db_fun(paste0("SELECT cum_id FROM CommunityUsageMetrics"))
  
  if (!(params$package %in% pkgs_in_db$cum_id)) {
    metric_cum_Info_upload_to_DB(params$package)
    riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
  } else{
    riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
  }
   
  time_since_first_release_info <- riskmetrics_cum$time_since_first_release[1] 
  time_since_version_release_info <-riskmetrics_cum$time_since_version_release[1]
  no_of_downloads_last_year_info <-
        riskmetrics_cum$no_of_downloads_last_year[1]
  
  riskmetrics_tm <-
    db_fun(
      paste0(
        "SELECT * FROM TestMetrics WHERE TestMetrics.tm_id ='",
        params$package,
        "'"
      )
    )
  riskmetrics_tm <- c(strsplit(riskmetrics_tm$test_coverage,",")[[1]][1], strsplit(riskmetrics_tm$test_coverage,",")[[1]][2])
  

   comment_mm <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'mm'"
        )
      )  
 
   comment_cum <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'cum'"
        )
      )

    comment_tm <-
      db_fun(
        paste0(
          "SELECT user_name, user_role, comment, added_on FROM Comments WHERE comm_id = '",
          params$package,
          "' AND comment_type = 'tm'"
        )
      )
    
    riskinfo <- package_info("riskmetric", dependencies = FALSE)
```

## Report of the " `r pkg_GenInfo$package` " Package: 

This **`r pkg_GenInfo$package`** package report was generated using riskmetric version **`r riskinfo$loadedversion`**

Metrics were reviewed via the R Package Risk Assessment Application.

```{r setup, include=FALSE}
library(knitr)
library(shiny)

knitr::opts_chunk$set(echo = F,fig.width=5.5, fig.height=3.4)

#Plot parameters
#define base_size of text
bsize_text <- 11

#define background color of plots
p_color <- 'white'

```


<hr style="
  height: 2px;
  border: none;
  color: #3c8dbc;
  background-color: #3c8dbc">



**Summary**

Score: `r pkg_GenInfo$score`
```{r echo=FALSE}
 if (!identical(pkg_GenInfo$decision, character(0)) && pkg_GenInfo$decision != "") {
    HTML(paste("<br>", "<h5>Overall risk: ", "<b>", pkg_GenInfo$decision, "</b></h5>"))
  } else{
    HTML(paste("<br>", "<h5><b>Overall risk: Pending</b></h5>"))
  }
```


**Overall Comments(`r nrow(comment_o)`):**

```{r echo=FALSE}
  comment_o <- data.frame(comment_o %>% map(rev))
  HTML(dsp_cmts(comment_o))
```
\newpage

## General Info

**Package:** `r pkg_GenInfo$package`

**Version:** `r pkg_GenInfo$version`

**Title:** `r pkg_GenInfo$title`

**Description:** `r pkg_GenInfo$description`

**Author:** `r pkg_GenInfo$author`

**Maintainer:** `r pkg_GenInfo$maintainer`

**License:** `r pkg_GenInfo$license`

**Published:** `r pkg_GenInfo$published`

\newpage

## Maintenance Metrics

```{r echo=FALSE}

Metric<-c("Presence of vignettes?","Associated website URL?","NEWS?","News is current?","Bugs publicly documented?","Bug closure","Documentation","Source code public?","Has a maintainer?")

Result<-c(
    if(package_has_vignettes[2] == -1){"NA"}
      else{ ifelse(package_has_vignettes[1] == 1, "YES", "NO")},
     if(package_has_website[2] == -1){"NA"}
      else{ ifelse(package_has_website[1] == 1, "YES", "NO")},
     if(package_has_news[2] == -1){"NA"}
      else{ ifelse(package_has_news[1] == 1, "YES", "NO")},
      if(news_is_current[2] == -1){"NA"}
      else{ ifelse(news_is_current[1] == 1, "YES", "NO")},
     if(has_bug_reports[2] == -1){"NA"}
      else{ ifelse(has_bug_reports[1] == 1, "YES", "NO")},
     if(status_of_last_30_reported_bugs[2] == -1){"NA"}
      else{paste0(status_of_last_30_reported_bugs[1],"%")},
     if(exported_objects_with_documentation[2] == -1){"NA"}
      else{paste0(exported_objects_with_documentation[1],"%")},
     if(source_code_is_public[2] == -1){"NA"}
      else{ ifelse(source_code_is_public[1] == 1, "YES", "NO")},
     if(has_a_package_maintainer[2] == -1){"NA"}
      else{ ifelse(has_a_package_maintainer[1] == 1, "YES", "NO")}
    )

Detail<-c(
          if(package_has_vignettes[2] == -1){"Metric is not applicable for this source of package"}
            else{paste("The package has", package_has_vignettes[2], "Vignettes")},
          if(package_has_website[2] == -1){"Metric is not applicable for this source of package"}
            else{ ifelse(package_has_website[1] == 1, paste("Website:",package_has_website[2]), "The package does not have an associated website URL")},
          if(package_has_news[2] == -1){"Metric is not applicable for this source of package"}
            else{ ifelse(package_has_news[1] == 1, "The package has a NEWS file.", "The package does not have a NEWS file")},
          if(news_is_current[2] == -1){"Metric is not applicable for this source of package"}
            else{ ifelse(news_is_current[1] == 1, "NEWS file contains entry for current version number", "NEWS file does not contains entry for current version number")},
          if(has_bug_reports[2] == -1){"Metric is not applicable for this source of package"}
            else{ ifelse(has_bug_reports[1] == 1, paste("Bug reports URL:", has_bug_reports[2]), "The Bugs are not publicly documented")},
          if(status_of_last_30_reported_bugs[2] == -1){"Metric is not applicable for this source of package"}
            else{"Percentage of last 30 bugs closed"},
          if(exported_objects_with_documentation[2] == -1){"Metric is not applicable for this source of package"}
            else{"Proportion of exported objects documented"},
          if(source_code_is_public[2] == -1){"Metric is not applicable for this soucre of package"}
            else{ ifelse(source_code_is_public[1] == 1, paste("Source code URL:", source_code_is_public[2]), "Package does not have a Source code URL")},
          if(has_a_package_maintainer[2] == -1){"Metric is not applicable for this soucre of package"}
              else{ ifelse(has_a_package_maintainer[1] == 1, has_a_package_maintainer[2], "Package does not have a Maintainer")}
)
table_infobox<-data.frame(Metric,Result,Detail)

knitr::kable(table_infobox, format='pandoc')

```

### Comments for Maintenance Metrics(`r nrow(comment_mm)`):

```{r echo=FALSE}
comment_mm <- data.frame(comment_mm %>% map(rev))
HTML(dsp_cmts(comment_mm))
```

\newpage

## Community Usage Metrics

```{r echo=FALSE}

Metric<-c("Package Maturity", "Version Maturity", "Download Count")

Result<-c(
     if(time_since_first_release_info == -1){"NA"}
      else{time_since_first_release_info},
     if(time_since_version_release_info == -1){"NA"}
      else{time_since_version_release_info},
     if(no_of_downloads_last_year_info == -1){"NA"}
      else{formatC(no_of_downloads_last_year_info, format="f", big.mark=",", digits=0)}
)

Detail<-c(
     if(time_since_first_release_info == -1){"Metric is not applicable for this source of package"}
       else{"Months since first release."},
     if(time_since_version_release_info == -1){"Metric is not applicable for this source of package"}
       else{"Months since version release."},
     if(no_of_downloads_last_year_info == -1){"Metric is not applicable for this source of package"}
       else{"Downloads in Last Year."}
)

table_infobox_cum<-data.frame(Metric,Result,Detail)

knitr::kable(table_infobox_cum, format='pandoc')

num_dwnlds_plot(data = riskmetrics_cum,
                    input_select_pack = params$package)

```

### Comments for Community Usage Metrics(`r nrow(comment_cum)`):

```{r echo=FALSE}
comment_cum <- data.frame(comment_cum %>% map(rev))
HTML(dsp_cmts(comment_cum))
```

\newpage

## Testing Metrics


```{r echo=FALSE}
  bands = data.frame(
    start = c(0, 40, 80),
    end = c(40, 80, 100),
    color = ifelse(riskmetrics_tm[2] != -1, c("#ea3838", "#ffac29", "#00CC00"), c("#808080", "#808080", "#808080")),
    stringsAsFactors = FALSE
  )
  bands2 = data.frame(
    start = c(0, 40, 80),
    end = c(40, 80, 100),
    color = ifelse(riskmetrics_tm[2] != -1, c("#ea3838", "#ffac29", "#00CC00"), c("#808080", "#808080", "#808080")),
    stringsAsFactors = FALSE
  )
  amAngularGauge(
    x = as.numeric(ifelse(riskmetrics_tm[1] == "NA", 0, riskmetrics_tm[1])),
    start = 0,
    end = 100,
    bands = bands,
    secondAxe = TRUE,
    start2 = 0,
    end2 = 100,
    bands2 = bands2
  )
```


### Comments for Testing Metrics(`r nrow(comment_tm)`):


```{r echo=FALSE}
comment_tm <- data.frame(comment_tm %>% map(rev))
HTML(dsp_cmts(comment_tm))
```






