---
title: '<span style=''color: steelblue;''>R Package Risk Assessment </span>'
author: '**Author (Role): `r params$username` (`r params$user_role `)**'
date: "**Report Date: `r format(Sys.time(), '%B %d, %Y')`**"
output:
  word_document
params:
  package: NA
  riskmetric_version: NA
  cwd: NA
  username: NA
  user_role: NA
always_allow_html: yes
---


```{r echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

setwd(params$cwd)

pkg_GenInfo = db_fun(paste0(
  "SELECT * FROM package WHERE name ='",
  params$package,
  "'"
))

comment_o <-
  db_fun(
    paste0(
      "SELECT * FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'o'"
    )
  )

package_id <- db_fun(paste0("SELECT id
                                  FROM package
                                  WHERE name = ", "'", params$package, "';"))

# Leave method if package not found.
# TODO: save this to the json file.
if(nrow(package_id) == 0){
  print("PACKAGE NOT FOUND.")
  return()
}

# Collect all the metric names and values associated to package_id.
values$riskmetrics_mm <- db_fun(paste0(
  "SELECT metric.name, package_metrics.value
        FROM metric
        INNER JOIN package_metrics ON metric.id = package_metrics.metric_id
        WHERE package_metrics.package_id = ", "'", package_id, "'", " AND ",
  "metric.class = 'maintenance' ;"))

for(i in 1:nrow(values$riskmetrics_mm))
  values[[values$riskmetrics_mm$name[i]]] <- values$riskmetrics_mm$value[i]

riskmetrics_cum <-
  db_fun(
    paste0(
      "SELECT * FROM CommunityUsageMetrics WHERE cum_id ='",
      params$package,
      "'"
    )
  )

pkgs_in_db <- db_fun(paste0("SELECT cum_id FROM CommunityUsageMetrics"))

if (!(params$package %in% pkgs_in_db$cum_id)) {
  metric_cum_Info_upload_to_DB(params$package)
  riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
} else{
  riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
}

time_since_first_release_info <- riskmetrics_cum$time_since_first_release[1] 
time_since_version_release_info <-riskmetrics_cum$time_since_version_release[1]
no_of_downloads_last_year_info <-
  riskmetrics_cum$no_of_downloads_last_year[1]

package_id <- db_fun(paste0("SELECT id FROM package WHERE name = ", "'", input$select_pack, "'", ";"))
metric_id <- db_fun(paste0("SELECT id FROM metric WHERE name = 'covr_coverage';"))
covr_coverage <- db_fun(
  paste0("SELECT value FROM package_metrics WHERE ",
         "package_id = ", package_id,
         " AND ",
         "metric_id = ", metric_id,
         ";"
  )
)
covr_coverage <- covr_coverage$value

comment_mm <-
  db_fun(
    paste0(
      "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'mm'"
    )
  )  

comment_cum <-
  db_fun(
    paste0(
      "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'cum'"
    )
  )

comment_tm <-
  db_fun(
    paste0(
      "SELECT user_name, user_role, comment, added_on FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'tm'"
    )
  )

```

## Report of the "`r pkg_GenInfo$name`" package:

This **`r pkg_GenInfo$name`** package report was generated using  **`r params$version`** riskmetric version .  Metrics were reviewed via the R Package Risk Assessment Application.</div>

```{r setup, include=FALSE}
library(knitr)
library(shiny)

knitr::opts_chunk$set(echo = F,fig.width=5.5, fig.height=3.4)

#Plot parameters
#define base_size of text
bsize_text <- 11

#define background color of plots
p_color <- 'white'

```


<hr style="
  height: 2px;
  border: none;
  color: #3c8dbc;
  background-color: #3c8dbc">

**Summary**

Score: `r pkg_GenInfo$score`
```{r echo=FALSE}
 if (!identical(pkg_GenInfo$decision, character(0)) && pkg_GenInfo$decision != "") {
    HTML(paste("<br>", "<h5>Overall risk: ", "<b>", pkg_GenInfo$decision, "</b></h5>"))
  } else{
    HTML(paste("<br>", "<h5><b>Overall risk: Pending</b></h5>"))
  }
```


**Overall Comments(`r nrow(comment_o)`):**

```{r echo=FALSE}
  comment_o <- data.frame(comment_o %>% map(rev))
table_o<-data.frame("User ID"=comment_o$user_name,"Role"= comment_o$user_role, "Time"= comment_o$added_on,"Comments"=comment_o$comment)
  
knitr::kable(table_o, format='pandoc')
  
```
\newpage

## General Info

**Package:** `r pkg_GenInfo$name`

**Version:** `r pkg_GenInfo$version`

**Title:** `r pkg_GenInfo$title`

**Description:** `r pkg_GenInfo$description`

**Author:** `r pkg_GenInfo$author`

**Maintainer:** `r pkg_GenInfo$maintainer`

**License:** `r pkg_GenInfo$license`

**Published:** `r pkg_GenInfo$published`

\newpage

## Maintenance Metrics

```{r echo=FALSE}

Metric <- c("Presence of vignettes?",
            "Associated website URL?",
            "NEWS?",
            "News is current?",
            "Bugs publicly documented?",
            "Bug closure",
            "Documentation",
            "Source code public?",
            "Has a maintainer?")

Result <- c(
  if(values$has_vignettes %in% c("NA", "pkg_metric_error")){"NA"}
  else{ifelse(values$has_vignettes != "0", "YES", "NO")},
  
  if(values$has_website == "pkg_metric_error"){"NA"}
  else{ifelse(values$has_website != "NA", "YES", "NO")},
  
  if(values$has_news %in% c("NA", "pkg_metric_error")){"NA"}
  else{ ifelse(values$has_news == "1", "YES", "NO")},
  
  if(values$news_current %in% c("NA", "pkg_metric_error")){"NA"}
  else{ifelse(values$news_current == "TRUE", "YES", "NO")},
  
  if(values$has_bug_reports_url == "pkg_metric_error"){"NA"}
  else{ifelse(values$has_bug_reports_url == "NA", "NO", "YES")},
  
  if(values$bugs_status %in% c("NA", "pkg_metric_error")){"NA"}
  else{paste0(values$bugs_status, "%")},
  
  if(values$export_help %in% c("NA", "pkg_metric_error")){"NA"}
  else{paste0(values$export_help, "%")},
  
  if(values$has_source_control == "pkg_metric_error"){"NA"}
  else{ ifelse(values$has_source_control == "NA", "NO", "YES")},
  
  if(values$has_maintainer %in% c("NA", "pkg_metric_error")){"NA"}
  else{ ifelse(values$has_maintainer != "", "YES", "NO")}
)

Detail <- c(
  if(values$has_vignettes %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    paste("The package has", values$has_vignettes,
          if(values$has_vignettes == "1") "vignette" else "vignettes"),
  
  if(values$has_website %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    ifelse(values$has_website != "NA", paste("Website:", values$has_website),
           "The package does not have an associated website URL"),
  
  if(values$has_news %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    paste("The package",
          ifelse(values$has_news == "1", "has", "does not have"),
          "a NEWS file"),
  
  if(values$news_current %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    paste("NEWS file",
          ifelse(values$news_current == "TRUE", "contains", "does not contain"),
          "an entry for the current version number"),
  
  if(values$has_bug_reports_url == "pkg_metric_error")
    "Metric is not applicable for this source of package"
  else
    ifelse(values$has_bug_reports_url != "NA",
           paste("Bug reports URL:", values$has_bug_reports_url),
           "The bugs are not publicly documented"),
  
  if(values$bugs_status %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else
    "Percentage of last 30 bugs closed",
  
  if(values$export_help %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this source of package"
  else{"Percentage of exported objects documented"},
  
  if(values$has_source_control == "pkg_metric_error")
    "Metric is not applicable for this soucre of package"
  else
    ifelse(values$has_source_control != "NA",
           paste("Source code URL:", values$has_source_control ),
           "Package does not have a source code URL"),
  
  if(values$has_maintainer %in% c("NA", "pkg_metric_error"))
    "Metric is not applicable for this soucre of package"
  else
    ifelse(values$has_maintainer != "",
           values$has_maintainer,
           "Package does not have a maintainer")
)

table_infobox<-data.frame(Metric, Result, Detail)
knitr::kable(table_infobox, format='pandoc')
```

### Comments for Maintenance Metrics(`r nrow(comment_mm)`):

```{r echo=FALSE}
comment_mm <- data.frame(comment_mm %>% map(rev))
    
table_mm<-data.frame("User ID"=comment_mm$user_name,"Role"= comment_mm$user_role, "Time"= comment_mm$added_on,"Comments"=comment_mm$comment)
  knitr::kable(table_mm, format='pandoc')

```

\newpage

## Community Usage Metrics

```{r echo=FALSE}

Metric<-c("Package Maturity", "Version Maturity", "Download Count")

Result<-c(
     if(time_since_first_release_info == -1){"NA"}
      else{time_since_first_release_info},
     if(time_since_version_release_info == -1){"NA"}
      else{time_since_version_release_info},
     if(no_of_downloads_last_year_info == -1){"NA"}
      else{formatC(no_of_downloads_last_year_info, format="f", big.mark=",", digits=0)}
)

Detail<-c(
     if(time_since_first_release_info == -1){"Metric is not applicable for this source of package"}
       else{"Months since first release."},
     if(time_since_version_release_info == -1){"Metric is not applicable for this source of package"}
       else{"Months since version release."},
     if(no_of_downloads_last_year_info == -1){"Metric is not applicable for this source of package"}
       else{"Downloads in Last Year."}
)

table_infobox_cum<-data.frame(Metric,Result,Detail)

knitr::kable(table_infobox_cum, format='pandoc')

num_dwnlds_plot(data = riskmetrics_cum,
                    input_select_pack = params$package)

```

### Comments for Community Usage Metrics(`r nrow(comment_cum)`):

```{r echo=FALSE}
comment_cum <- data.frame(comment_cum %>% map(rev))
  
table_cum<-data.frame("User ID"=comment_cum$user_name,"Role"= comment_cum$user_role, "Time"= comment_cum$added_on,"Comments"=comment_cum$comment)
  knitr::kable(table_cum, format='pandoc')
  
```
<!--

\newpage
## Testing Metrics


# ```{r echo=FALSE}
#   bands = data.frame(
#     start = c(0, 40, 80),
#     end = c(40, 80, 100),
#     color = ifelse(covr_coverage != "pkg_metric_error",
#                    c("#ea3838", "#ffac29", "#00CC00"),
#                    c("#808080", "#808080", "#808080")),
#     stringsAsFactors = FALSE
#   )
#   bands2 = data.frame(
#     start = c(0, 40, 80),
#     end = c(40, 80, 100),
#     color = ifelse(covr_coverage != "pkg_metric_error",
#                    c("#ea3838", "#ffac29", "#00CC00"),
#                    c("#808080", "#808080", "#808080")),
#     stringsAsFactors = FALSE
#   )
#   amAngularGauge(
#     x = as.numeric(ifelse(covr_coverage == "NA", 0, covr_coverage)),
#     start = 0,
#     end = 100,
#     bands = bands,
#     secondAxe = TRUE,
#     start2 = 0,
#     end2 = 100,
#     bands2 = bands2
#   )
# ```
-->

<!-- ### Comments for Testing Metrics(`r nrow(comment_tm)`):  -->

<!-- ```{r echo=FALSE} -->
<!-- comment_tm <- data.frame(comment_tm %>% map(rev)) -->
<!-- table_tm<-data.frame("User ID"=comment_tm$user_name,"Role"= comment_tm$user_role, "Time"= comment_tm$added_on,"Comments"=comment_tm$comment) -->
<!--  knitr::kable(table_tm, format='pandoc') -->
<!-- ``` -->
