---
title:   "<span style='color: steelblue;'>R Package Risk Assessment </span>"
subtitle: "R Validation Hub"
author: "<br><span style='font-weight:bold'>Author (Role): </span> `r input$name` (`r input$role `)"
date: "<span style='font-weight:bold'>Report Date: </span>`r format(Sys.time(), '%B %d, %Y')`"
always_allow_html: true
output: html_document
runtime: shiny
params:
  package: NA
  version: NA
  cwd: NA
---


```{r  echo=FALSE,warning=FALSE }

setwd(params$cwd)

pkg_GenInfo = db_fun(paste0(
  "SELECT * FROM package WHERE name ='",
  params$package,
  "'"
))

comment_o <-
  db_fun(
    paste0(
      "SELECT * FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'o'"
    )
  )

package_id <- db_fun(paste0("SELECT id
                                  FROM package
                                  WHERE name = ", "'", params$package, "';"))

# Leave method if package not found.
# TODO: save this to the json file.
if(nrow(package_id) == 0){
  print("PACKAGE NOT FOUND.")
  return()
}

# Collect all the metric names and values associated to package_id.
values$riskmetrics_mm <- db_fun(paste0(
  "SELECT metric.name, package_metrics.value
        FROM metric
        INNER JOIN package_metrics ON metric.id = package_metrics.metric_id
        WHERE package_metrics.package_id = ", "'", package_id, "'", " AND ",
  "metric.class = 'maintenance' ;"))

for(i in 1:nrow(values$riskmetrics_mm))
  values[[values$riskmetrics_mm$name[i]]] <- values$riskmetrics_mm$value[i]

riskmetrics_cum <-
  db_fun(
    paste0(
      "SELECT * FROM CommunityUsageMetrics WHERE cum_id ='",
      params$package,
      "'"
    )
  )

pkgs_in_db <- db_fun(paste0("SELECT cum_id FROM CommunityUsageMetrics"))

if (!(params$package %in% pkgs_in_db$cum_id)) {
  metric_cum_Info_upload_to_DB(params$package)
  riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
} else{
  riskmetrics_cum <- db_fun( paste0("SELECT * FROM CommunityUsageMetrics WHERE cum_id ='", params$package, "'") )
}

time_since_first_release_info <- riskmetrics_cum$time_since_first_release[1] 
time_since_version_release_info <- riskmetrics_cum$time_since_version_release[1]
no_of_downloads_last_year_info <-
  riskmetrics_cum$no_of_downloads_last_year[1]


metric_id <- db_fun(paste0("SELECT id FROM metric WHERE name = 'covr_coverage';"))
covr_coverage <- db_fun(
  paste0("SELECT value FROM package_metrics WHERE ",
         "package_id = ", package_id,
         " AND ",
         "metric_id = ", metric_id,
         ";"
  )
)
covr_coverage <- covr_coverage$value


comment_mm <-
  db_fun(
    paste0(
      "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'mm'"
    )
  )  

comment_cum <-
  db_fun(
    paste0(
      "SELECT user_name, user_role, comment, added_on  FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'cum'"
    )
  )

comment_tm <-
  db_fun(
    paste0(
      "SELECT user_name, user_role, comment, added_on FROM Comments WHERE comm_id = '",
      params$package,
      "' AND comment_type = 'tm'"
    )
  )

```


<div class="heading_report"> Report of the "`r pkg_GenInfo$name`" Package:</div>

<div class="report">This **`r pkg_GenInfo$name`** package report was generated using  **`r params$version`** riskmetric version. Metrics were reviewed via the R Package Risk Assessment Application.</div>



```{r setup, include=FALSE}
library(knitr)
library(shiny)
library(shinyjs)

knitr::opts_chunk$set(echo = F,fig.width=5.5, fig.height=3.4)

#Plot parameters
#define base_size of text
bsize_text <- 11

#define background color of plots
p_color <- 'white'

```


<hr style="
  height: 2px;
  border: none;
  color: #3c8dbc;
  background-color: #3c8dbc">

<div class="blue para-header">Summary</div>

**Score:** `r pkg_GenInfo$score`
```{r echo=FALSE}
 if (!identical(pkg_GenInfo$decision, character(0)) && pkg_GenInfo$decision != "") {
    HTML(paste("<br>", "<h5>Overall risk: ", "<b>", pkg_GenInfo$decision, "</b></h5>"))
  } else{
    HTML(paste("<br>", "<h5><b>Overall risk: Pending</b></h5>"))
  }
```

**Overall Comments(`r nrow(comment_o)`):**
<div class="col-md-12 comments-box">

```{r echo=FALSE}

  comment_o <- data.frame(comment_o %>% map(rev))
   HTML(paste(
      "<div class='col-sm-12 comment-border-bottom'><i class='fa fa-user-tie fa-2x d-inline'></i><h3 class='ml-3 d-inline'><b class='user-name-color'>",
      comment_o$user_name,
      "(",
      comment_o$user_role,
      ")",
      "</b><sub>",
      comment_o$added_on,
      "</sub></h3><h4 class='ml-3 lh-4'>",
      comment_o$comment,
      "</h4></div>"
    ))
```
</div>
<div class="blue para-header">General Info</div>

**Package:** `r pkg_GenInfo$name`

**Version:** `r pkg_GenInfo$version`

**Title:** `r pkg_GenInfo$title`

**Description:** `r pkg_GenInfo$description`

**Author:** `r pkg_GenInfo$author`

**Maintainer:** `r pkg_GenInfo$maintainer`

**License:** `r pkg_GenInfo$license`

**Published:** `r pkg_GenInfo$published`

<div class="blue para-header mb-4">Maintenance Metrics</div>

```{r echo=FALSE, results="asis"}
div(
class = "row mb-3",
  has_vignettes_infobox(values),
  has_website_infobox(values),
  has_news_infobox(values)
)
```

```{r echo=FALSE}
div(
class = "row mb-3",
  news_current_infobox(values),
  has_bug_reports_url_infobox(values),
  bugs_status_infobox(values)
)
```    

```{r echo= FALSE}
div(
  class = "row mb-3",
  export_help_infobox(values),
  has_source_control_infobox(values),
  has_maintainer_infobox(values)
)

```

<div class="row col-md-12 comments">Comments for Maintenance Metrics(`r nrow(comment_mm)`):</div>
<div class="col-md-12 comments-box">

```{r echo=FALSE}
comment_mm <- data.frame(comment_mm %>% map(rev))
    HTML(paste(
      "<div class='col-sm-12 comment-border-bottom single-comment-div'><i class='fa fa-user-tie fa-2x d-inline'></i><h3 class='ml-3 d-inline'><b class='user-name-color'>",
      comment_mm$user_name,
      "(",
      comment_mm$user_role,
      ")",
      "</b><sub>",
      comment_mm$added_on,
      "</sub></h3><h4 class='ml-3 lh-4'>",
      comment_mm$comment,
      "</h4></div>"
 ))

```

</div>
<div class="row col-md-12 blue mb-4 para-header">Community Usage Metrics</div>

```{r echo=FALSE}
  
  infoBox(
    title = "Package Maturity",
    time_since_first_release_info,
    subtitle = ifelse(time_since_first_release_info != "NA",
                      "Months since first release.",
                      "Metric is not applicable for this source of package."),
    icon = shiny::icon("calendar"),
    width = 3,
    fill = TRUE
  )

  infoBox(
    title = "Version Maturity",
    time_since_version_release_info,
    subtitle = ifelse(time_since_version_release_info != "NA", 
                      "Months since version release.",
                      "Metric is not applicable for this source of package."),
    icon = shiny::icon("calendar"),
    width = 3,
    fill = TRUE
  )
  
  infoBox(
    title = "Download Count",
    formatC(no_of_downloads_last_year_info, format="f", big.mark=",", digits=0),
    subtitle = ifelse(no_of_downloads_last_year_info != "NA", 
                      "Downloads in Last Year",
                      "Metric is not applicable for this source of package."),
    icon = shiny::icon("signal"),
    width = 3,
    fill = TRUE
  )
  


```

<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>

<div style="margin-top: 100px"></div>
```{r echo=FALSE}
p <- num_dwnlds_plot(data = riskmetrics_cum,
                    input_select_pack = params$package)
tagList(p)
```


```{r echo=FALSE}

if (riskmetrics_cum$no_of_downloads_last_year[1] == 0) {
  tags$script(
    HTML(
      "setTimeout(function(){
         var element = document.getElementsByClassName('highcharts-container ')[0].getElementsByClassName('highcharts-subtitle');
        element[0].style.fontSize = '16px';
        var xVal = element[0]['x'].baseVal[0].value;
        element[0]['y'].baseVal[0].value = xVal/2;
      },500)"
    )
  )
}
```

<div class="row col-md-12 comments">Comments for Community Usage Metrics(`r nrow(comment_cum)`):</div>
<div class="col-md-12 comments-box">

```{r echo=FALSE}
comment_cum <- data.frame(comment_cum %>% map(rev))
   HTML(paste(
      "<div class='col-sm-12 comment-border-bottom'><i class='fa fa-user-tie fa-2x d-inline'></i><h3 class='ml-3 d-inline'><b class='user-name-color'>",
      comment_cum$user_name,
      "(",
      comment_cum$user_role,
      ")",
      "</b><sub>",
      comment_cum$added_on,
      "</sub></h3><h4 class='ml-3 lh-4'>",
      comment_cum$comment,
      "</h4></div>"
    ))
```
<!--
# </div>
# <div class="blue para-header">Testing Metrics</div>
# 
# <br>
# 
# ```{r echo=FALSE} 
# 
#   bands = data.frame(
#     start = c(0, 40, 80),
#     end = c(40, 80, 100),
#     color = ifelse(covr_coverage != "pkg_metric_error",
#                    c("#ea3838", "#ffac29", "#00CC00"),
#                    c("#808080", "#808080", "#808080")),
#     stringsAsFactors = FALSE
#   )
#   bands2 = data.frame(
#     start = c(0, 40, 80),
#     end = c(40, 80, 100),
#     color = ifelse(covr_coverage != "pkg_metric_error",
#                    c("#ea3838", "#ffac29", "#00CC00"),
#                    c("#808080", "#808080", "#808080")),
#     stringsAsFactors = FALSE
#   )
#   amAngularGauge(
#     x = as.numeric(ifelse(covr_coverage == "NA", 0, covr_coverage)),
#     start = 0,
#     end = 100,
#     bands = bands,
#     secondAxe = TRUE,
#     start2 = 0,
#     end2 = 100,
#     bands2 = bands2
#   )
# ```

# ```{r echo=FALSE}
# 
# if(covr_coverage == "pkg_metric_error"){
#   tags$script(HTML(
#   "
#   setTimeout(function() {
#     var elementCircle = document.getElementsByClassName('ramcharts_base')[0].getElementsByTagName('circle')[0];
#     elementCircle.nextSibling.remove();
#     elementCircle.remove();
#     var element = document.getElementsByClassName('ramcharts_base')[0].getElementsByTagName('svg')[0];
#     var textElement = document.createElementNS('http://www.w3.org/2000/svg', 'text');
#     textElement.setAttributeNS(null, 'x', element.width.baseVal.value/2);
#     textElement.setAttributeNS(null, 'y', element.height.baseVal.value/2 +20);
#     textElement.setAttributeNS(null,'font-size','20');
#     textElement.setAttributeNS(null,'fill','red');
#     textElement.setAttributeNS(null,'text-anchor','middle');
#     textElement.setAttributeNS(null,'class','gauge-error-text');
#     var txt = document.createTextNode('Metric is not applicable');
#     textElement.appendChild(txt);
#     element.appendChild(textElement);
#     
#     var textElement2 = document.createElementNS('http://www.w3.org/2000/svg', 'text');
#     textElement2.setAttributeNS(null, 'x', element.width.baseVal.value/2);
#     textElement2.setAttributeNS(null, 'y', element.height.baseVal.value/2 +50);
#     textElement2.setAttributeNS(null,'font-size','20');
#     textElement2.setAttributeNS(null,'fill','red');
#     textElement2.setAttributeNS(null,'text-anchor','middle');
#     textElement2.setAttributeNS(null,'class','gauge-error-text');
#     var txt2 = document.createTextNode('for this source of package');
#     textElement2.appendChild(txt2);
#     element.appendChild(textElement2);
#     var allEle = element.querySelectorAll('text')
#     for(let i=0; i<allEle.length; i++){
#       if(allEle[i].textContent == 100 && allEle[i+1].textContent == 0){
#           allEle[i+1].textContent = 'NA';
#       }
#     }
#   }, 1000)
#   "
#   ))
# }
# ```
-->
<!-- <br> -->
<!-- <div class="row col-md-12 comments">Comments for Testing Metrics(`r nrow(comment_tm)`):</div> -->

<!-- <style> -->
<!-- .user-name-color { -->
<!-- color: #7f7f7f; -->
<!-- } -->
<!-- .ml-3 { -->
<!--     margin-left: 1rem!important; -->
<!--     font-size: 17px; -->
<!-- } -->
<!-- .comment-border-bottom { -->
<!--   padding:0px; -->
<!--   border-bottom: 1px solid rgba(0,0,0,.125); -->
<!--   margin-bottom: 2rem; -->
<!-- } -->

<!-- .fa-user-tie { -->
<!--   color: rgba(77,141,201,.70); -->
<!--   top: 35%; -->
<!--   left: 0px; -->
<!-- } -->

<!-- .blue { -->
<!--     color: steelblue; -->
<!--     font-size: 30px; -->
<!-- } -->
<!-- .comments{ -->
<!--   color:steelblue; -->
<!--   font-size:22px; -->
<!--   margin-top: 2rem; -->
<!-- } -->
<!-- .report{ -->
<!-- font-size:14px -->
<!-- color: steelblue; -->
<!-- } -->
<!-- .heading_report { -->
<!--     font-size: 23px; -->
<!--     font-weight: bold; -->

<!-- } -->
<!-- .d-inline { -->
<!--   display: inline; -->
<!-- } -->

<!-- .info-box-content, .info-box-icon { -->
<!--   display: inline; -->
<!-- } -->

<!-- .glyphicon-thumbs-up { -->
<!--   padding: 3px; -->
<!-- } -->

<!-- .glyphicon-thumbs-down { -->
<!--   padding: 3px; -->
<!-- } -->

<!-- .fa-bar-chart, .fa-calendar { -->
<!--   padding: 3px; -->
<!-- } -->

<!-- .mb-3 { -->
<!--   margin-bottom: 1rem; -->
<!-- } -->

<!-- .mb-4 { -->
<!--   margin-bottom: 1.5rem; -->
<!-- } -->

<!-- .comments-box { -->
<!--   max-height: 300px; -->
<!--   overflow-y: auto; -->
<!--   padding: 10px; -->
<!--   border: 1px solid rgb(0, 0, 0.125); -->
<!--   margin-bottom: 2rem; -->
<!-- } -->
<!-- .amcharts-chart-div > a { -->
<!--   display: none !important; -->
<!-- } -->
<!-- .info-box-number { -->
<!--   font-weight: bold; -->
<!-- } -->
<!-- .title.toc-ignore { -->
<!--   text-align: center; -->
<!-- } -->
<!-- .para-header{ -->
<!--   text-align: left; -->
<!--   text-decoration: none; -->
<!--   text-underline-position: under; -->
<!-- } -->

<!-- .highcharts-container { -->
<!--   margin-top: 3rem; -->
<!-- } -->

<!-- .icon-color-grey::before { -->
<!--   color: grey; -->
<!-- } -->

<!-- </style> -->

<!-- <div class="col-md-12 comments-box"> -->

<!-- ```{r echo=FALSE} -->
<!--     comment_tm <- data.frame(comment_tm %>% map(rev)) -->
<!--     HTML(paste( -->
<!--       "<div class='col-sm-12 comment-border-bottom'><i class='fa fa-user-tie fa-2x d-inline'></i><h3 class='ml-3 d-inline'><b class='user-name-color'>", -->
<!--       comment_tm$user_name, -->
<!--       "(", -->
<!--       comment_tm$user_role, -->
<!--       ")", -->
<!--       "</b><sub>", -->
<!--       comment_tm$added_on, -->
<!--       "</sub></h3><h4 class='ml-3 lh-4'>", -->
<!--       comment_tm$comment, -->
<!--       "</h4></div>" -->
<!--     )) -->

<!-- ``` -->
<!-- </div> -->

